ropenblas: Download, Compile and Link OpenBLAS Library with R

### 2021-03-11 paper/paper.Rmd
Update

Table 1 below presents the benefit of considering an optimized version of BLAS. Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (function `svd()`) and in the calculation of the inverse of that same matrix (function `solve()`). Some repetitions (100 repetitions) of each of the respective functions were performed. The benchmark can be better observed through the violin plots shown in Figure 2.

@@

| Functions  | Library  | Time (seconds) |
|----------- |----------|:---------------:|
| `svd(x)`   | BLAS     | 6.520      |
| `svd(x)`   | OpenBLAS | 0.641     |
| `solve(x)` | BLAS     | 1.640      |
| `solve(x)` | OpenBLAS | 0.640      |
: Comparison of the computational costs of the `svd()` and `solve()` functions.

>>>>

Table 1 below presents the benefit of considering an optimized version of BLAS. Computational costs are presented in the calculation of the singular decomposition in a rectangular matrix (`svd()`) and in the calculation of the inverse of that same matrix (`solve()` function). Some repetitions (100 repetitions) of each of the respective functions were performed. The benchmark can be better observed through the violin plots shown in Figure 2.

@@

| Functions  | Library  | Time (seconds) |
|----------- |----------|:---------------:|
| `svd(x)`   | BLAS     | 6.520      |
| `svd(x)`   | OpenBLAS | 0.641     |
| `solve(x)` | BLAS     | 1.640      |
| `solve(x)` | OpenBLAS | 0.640      |
: Comparison of the computational costs of the `svd()` and `solve()` functions (average of 100 repetitions).
